Computing astrophysical inferences with diffusive nested sampling

### 2014-03-20 ms.tex
Paragraph

Recently we investigated a Bayesian approach for finding objects in ``crowded
fields'', small patches of the sky where many stars are visible in an image.
Each star would appear as a point source in the image, except for the effects
of blurring (caused by either diffraction as the light enters the telescope,
or by atmospheric fluctuations), and the images are also typically noisy.

@@

\begin{theacknowledgments}
It is a pleasure to thank David W. Hogg (NYU), Daniel Foreman-Mackey (NYU),
Fengji Hou (NYU), Anna Pancoast (UCSB), and
John Skilling (MaxEnt Data Consultants) for valuable discussions.
\end{theacknowledgments}

>>>>

Recently we investigated a Bayesian approach for finding objects in ``crowded
fields'', small patches of the sky where many stars are visible in an image.
Each star would appear as a point source in the image, except for the effects
of blurring (caused by either diffraction as the light enters the telescope,
or by atmospheric fluctuations), and the images are also typically noisy.
Since the number of stars $N$ is itself unknown, we use reversible jump
MCMC {\it within} DNS to infer $N$.

For the ``easy'' simulated data set containing 100 stars, the information
$H$ was approximately 500 nats, whereas for the ``hard'' dataset the information
was $\sim$2600 nats. In both cases, the upward part of the DNS run was
straightforward. However, in the ``hard'' case the diffusion phase of DNS
is very slow. Unfortunately, I am presently unaware of any Nested Sampling
method that only moves upwards in likelihood but is able to correct for the
use of imperfect MCMC. Variations of annealing or tempering such as
``annealed importance sampling'' and ``linked importance sampling'' \citep{ais, lis}
have both these properties, suggesting this may be possible with NS as well.

@@

\begin{theacknowledgments}
It is a pleasure to thank David W. Hogg (NYU), Daniel Foreman-Mackey (NYU),
Fengji Hou (NYU), Anna Pancoast (UCSB), Benjamin Pope (Oxford), and
John Skilling (MaxEnt Data Consultants) for valuable discussions.
\end{theacknowledgments}
